On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-09 Manuscript/manuscript.tex
further comments and edits

% control floats
%% \renewcommand\floatpagefraction{.9}
%% \renewcommand\topfraction{.9}
%% \renewcommand\bottomfraction{.9}
%% \renewcommand\textfraction{.2}
%% \setcounter{totalnumber}{50}
%% \setcounter{topnumber}{50}
%% \setcounter{bottomnumber}{50}

@@

\section*{introduction}

Block bootstrap is a tool to construct confidence intervals (CI) to make
inferences about dependent data. Essentially, it depends on correct estimation
of the uncertainty in the estimation, similar to the standard bootstrap 
\citep{efron1979bootstrap}, but for serially dependent data.
Early ideas of block bootstrap were developed not long after the standard 
bootstrap.\citep{hall1985resampling, carlstein1986use,kunsch1989jackknife} It 
has since
been applied in various fields, for instance, econometrics and 
meteorology.\citep{mackinnon2006bootstrap, varga2017generalised}
Block bootstrap is especially useful for serially dependent data when the serial 
dependence is not specified or not of primary interest. The method is expected 
to produce CIs with coverage rates matching their nominal levels as the sample 
size grows. However, when dealing with finite sample sizes, an important 
question is how large the sample size must be for block bootstrap CIs to have 
the desired coverage rates.
%\eds{I think the superscript citations need to go before the punctuation.  
%Please check in other AJUR papers and adjust throughout the paper if needed.}
%\mc{from the style guide: "Please bold and superscript the numbers for 
%references in the text.1 Separate superscripted numbers by comma and space,1, 2 
%they should be separated by an en-dash if the consecutive list of more than two 
%numbers is used.1–3 List them AFTER punctuation (be it comma or period) with no 
%space.2} 
%\eds{thank you for checking!}

@@

\eds{If we include all these drawbacks here, we need to also provide some good 
features of block bootstrap as well, otherwise, why do we care about their CI 
performance?}
\mc{addressed}

@@

\section*{block bootstrap cis}
\label{sec:bbci}

@@

\paragraph{Standard Normal CI}
Assuming that $\hat\theta_n$ is asymptotically normally distributed with 
$\theta$ as the mean, we just need an estimate of the standard error to 
construct an approximate CI.\citep{efron1993introduction} Let
$\widehat{\text{SE}}$ be the empirical standard error of the bootstrap point 
estimates $\hat\theta_n^{(b)}$ for $b \in \{1, \ldots, B\}$. Let $z_{(\alpha)}$ 
be the quantile function $F^{-1}(\alpha)$ of the standard normal distribution. 
A $(1 - \alpha)100\%$ standard normal CI is
\[
(\hat{\theta}_{n} - z_{(1-\alpha/2)}\widehat{\text{SE}}, \quad
\hat{\theta}_{n} - z_{(\alpha/2)}\widehat{\text{SE}}).
\]
%\eds{If $z_{(\alpha)}$ is the upper quantile, then $z_{(\alpha/2)}$ will be 
%positive and $z_{(1-\alpha/2)}$ will be negative for small $\alpha$ values; with
%the subtraction of the quantiles, the smaller CI endpoint would appear to
%be listed first.  Please check this notation, and the notation for Student's $t$ 
%CI, and other intervals which use the $z_{(\alpha)}$ upper standard normal 
%quantile.} 
%\mc{Replaced upper quantile with quantile function}

This CI is centered by the original point estimate $\hat\theta_n$ and is 
symmetric. The standard CI is classified by \citet{efron1993introduction} 
as a confidence interval based on bootstrap ``tables", which essentially means 
it is based on an asymptotic 
distribution with an estimated asymptotic variance (standard error). Its 
validity relies on whether the distribution of $\hat\theta_n$ is reasonably well 
approximated by its asymptotic normal distribution and whether the bootstrap
$\widehat{\text{SE}}$ approximates the true standard error.

\paragraph{Student's $t$ CI}
The procedure for constructing a Student's $t$ CI based on standard bootstrap is 
described in \citet{efron1993introduction}. Let $t_{(\alpha, k)}$ be the 
quantile function $F^{-1}(\alpha, k)$ of a $t$ distribution with $k$ degrees of 
freedom. With 
block bootstrapping, 
a $(1 - \alpha)100\%$ Student's $t$ CI is
\[
(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}\widehat{\text{SE}}, \quad
\hat{\theta}_{n} - t_{(\alpha/2), k -1}\widehat{\text{SE}}),
\]
%\eds{define $t_{(.)}$ and check the signs}  \mc{addressed}
where $k$ is the number of blocks. This CI is centered by the original point 
estimate $\hat\theta_n$ and is symmetric. Like the standard normal interval, the
Student's $t$ CI is classified by \citet{efron1993introduction} 
as a confidence interval based on bootstrap ``tables". In this case, its 
validity relies on whether the distribution of $\hat\theta_n$ is reasonably well 
approximated by the $t_{k-1}$ distribution with an expected value of $\theta$ 
and whether the bootstrap $\widehat{\text{SE}}$ approximates the true standard 
error.

@@

\paragraph{Bias-Corrected (BC) CI}
The procedure for constructing a bias-corrected Bootstrap CI based on standard
bootstrap is described in \citet{carpenter2000bootstrap}. Let
$\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for
$b \in \{1, \ldots, B\}$. Define 
$\alpha_1 = \Phi(2\hat{z}_0 - z_{1 - \alpha/2})$ 
and $\alpha_2 = \Phi(2\hat{z}_0 - z_{\alpha/2})$. 
A $(1 - \alpha)100\%$ ~BC CI is
\[
(\hat\theta_{n, \alpha_1}^{B}, \quad \hat\theta_{n, \alpha_2}^{B}).
\]
%\eds{the $z_{\alpha/2}$ and $z_{1 - \alpha/2}$ may need to be switched now in 
%$\alpha_1$ and $\alpha_2$ with the quantile definition for $z_{\alpha}$ -- 
%please check.} 
%\mc{yes they had to be switched}

\paragraph{Bias-Corrected and Accelerated (BCA) CI}
The BCA CI was first suggested in \citet{efron1987better}. Let $Z_{(i)}$ be the 
original sample without the $i$th block $z_i$ for $i \in \{1, \ldots, k\}$, let 
$\hat{\theta}_{(i)}$ be the statistic of $Z_{(i)}$, and let 
$\hat{\theta}_{(.)} = k^{-1}\sum_{i=1}^{k} \hat{\theta}_{(i)}$. 
Let
\begin{equation*}
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^2\}^{3/2}}.
\end{equation*}
Define
\begin{equation*}
\alpha_1 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
  z_{\alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{\alpha/2})}\right)
\end{equation*}
and
\begin{equation*}
\alpha_2 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{1 - \alpha/2})}\right).
\end{equation*}
%\eds{please check $z_{\alpha/2}$ and $z_{1 - \alpha/2}$ in 
%$\alpha_1$ and $\alpha_2$ with the quantile definition for $z_{\alpha}$} 
%\mc{this one is okay}
A $(1 - \alpha)100\%$ ~BCA CI is
\[
(\hat\theta_{n, \alpha_1}^{B}, \quad \hat\theta_{n, \alpha_2}^{B}).
\]
This CI is not necessarily centered by $\hat\theta_n$. The BCA method corrects 
for bias and skewness of the $B$ bootstrap point estimates 
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including 
bias-correction and acceleration factors. The acceleration factor refers to the 
rate of change of the standard error of $\hat\theta_n$ with respect to $\theta$.

@@

\section*{simulation design}
\label{sec:simdes}

%\subsection*{Design}

\eds{We compared the performance of the different block bootstrap CI methods 
under two marginal distributions: normal and exponential.}

\subsection*{Marginal Standard Normal Distribution}
%We designed a simulation study to compare the performance of the different block 
%bootstrap CI methods. In particular, 
We generated time series $X_t$ from a 1st 
order autoregressive (AR(1)) process:
\begin{equation*}
X_t = \phi X_{t-1} + \epsilon_t,
\end{equation*}
where $\phi$ is an autoregressive coefficient, and $\epsilon_t$ is a series of
independent errors from a normal distribution with mean zero and variance
$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
$\phi$, which was set to five levels: $\{-0.4, -0.2, 0.0, 0.2, 0.4\}$. We only
used serial dependences as strong as 0.4, because we only seek to 
establish the 
general trend as the strength of the autocorrelation 
increases, and how it varies depending on the sign of the autocorrelation and 
the parameter of interest. The 
series $X_t$ has mean zero and variance 
$\sigma_x^2 = (1 - \phi^2) \sigma_{\epsilon}^2$, so for each value of $\phi$, we 
set $\sigma_{\epsilon}^2 = 1 / (1 - \phi^2)$ such that $\sigma_x^2 = 1$.

Three target parameters of $X_t$ were considered:
1) $\mu = 0$, the mean of $X_t$;
2) $\sigma_x = 1$, the standard deviation of $X_t$; and
3) $\phi$, the lag-1 autocorrelation coefficient.
To investigate the effect of sample size~$n$, we considered an array of values
$n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we generated 
10000 replicates. The 
block bootstrap sampling step was done with function \texttt{tsboot} from R 
package \textsl{boot},\citep{boot} with block size $\lceil n / l \rceil$. This 
function by default is an implementation of moving block bootstrap as described 
in the previous section, meaning that that blocks are allowed to wrap around, 
and we tried both $l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$,
keeping the order of the block size constant but varying the coefficient. 
For each replicate, we constructed 
six 95\% block bootstrap 
CIs for each parameter as described in the last section with $B = 1000$. We can 
estimate $\mu$, 
$\sigma_x$, and $\phi$ by computing the sample mean, sample standard deviation, 
and lag-1 autocorrelation, respectively, of each bootstrap sample. Then we can 
construct intervals for each parameter using the appropriate procedures 
described in \textit{Block Bootstrap CIs}. 
Then we estimated their actual coverage 
rates along with their 95\% confidence intervals from the 10000 replicates.

The coverage rates of the CIs were used to compare the performance of CIs. Let
$\hat\theta_{L, r}$ and $\hat\theta_{U, r}$ be the lower and upper bound,
respectively, for the confidence interval constructed for each replicate
$r \in \{1, \ldots, R\}$, where $R$ is the number of replicates. Then
$cov = \#\{\hat\theta_{L, r} < \theta < \hat\theta_{U, r} \}/R$, for
$r \in \{1, \ldots, R\}$. If a CI method is valid, then the coverage rate is
expected to match the nominal level. Because it is unlikely for the coverage to 
exactly match the nominal level, we can construct a 95\% Wald-type CI of the 
coverage rate 
(which is an estimate of a proportion with $R = 10000$). If the proportion 0.95 
is included in the interval, the block bootstrap method is likely performing 
well. If all values in the interval are below 0.95, the results would suggest 
that the method either is providing inaccurate estimation, is underestimating 
the process' variability, or a combination of both. If all values in the 
interval are above .95, the results suggest that the method is overestimating 
the process' variability. \citet{brown2001interval} notes that the Wald-type 
interval has poor coverage as the proportion approaches 0 or 1.
\textbf{Figure~\ref{fig:norm1}} 
summarizes the empirical coverage rates and the 95\% confidence intervals of the 
real coverage for a marginal standard normal distribution using block bootstrap
with $l = \lceil n^{1/3} \rceil$, generated using the 
R \textsl{ggplot2} package.\citep{ggplot2}

\subsection*{Marginal Unit Exponential Distribution}
Additionally, we evaluated the performance of block bootstrap when used to 
estimate
the mean, standard deviation, and the lag-1 autocorrelation coefficient of a
stationary series with a marginal exponential distribution. The motivation of
for this study was to investigate if the results are robust to nonnormal
marginal distributions.

It is important to note that we expect the CIs that are based on bootstrap 
``tables" to depend on the 
asymptotic distribution of the statistics, but we expect such CIs to 
have similar performance for different error structures. For example, under the 
Central
Limit Theorem, we expect the asymptotic distribution of the sample mean to be 
approximately 
normal for both marginal normal distributions and marginal exponential 
distributions. Therefore, we do not expect CIs that are percentile-based
(Percentile, BC, BCA, Recentered Percentile CI) to perform better under
non-normal error structures.

The series were generated by marginally transforming the
AR(1) series $X_t$ in the simulation study by
\begin{equation*}
W_t = F^{-1}[\Phi(X_t)],
\end{equation*}
where $F^{-1}(p)$ is the quantile function for the unit exponential 
distribution. The true mean ($\mu$) and standard deviation ($\sigma_w$) 
parameters 
of $W_t$ are~1. The 
lag-1
autocorrelation coefficient is not invariant to the
transformation, \citep{hofert2018elements} but its value can be obtained by
\begin{equation*}
\int_{-\infty}^\infty \int_{-\infty}^\infty F^{-1}[\Phi(x)] F^{-1}[\Phi(y)] g_2(x, y; \phi) \dd x \dd y - 1,
\end{equation*}
where $g_2(x, y; \phi)$ is the density of a standard bivariate normal
distribution with correlation parameter~$\phi$. We kept the configuration of
$\phi \in \{-0.4, -0.2, 0.0, 0.2, 0.4\}$, and the corresponding lag-1
autocorrelation coefficients are $\{-0.298, -0.156, \allowbreak 0, 0.170, 0.355\}$.

For a marginal exponential  distribution, the empirical coverage rates for 
$\mu$, $\sigma_w$, %\eds{define $\sigma_w$} 
%\mc{added definitions for $\mu$ and $\sigma_w$ in the above paragraph} 
and 
the lag-1 autocorrelation coefficient using block bootstrap
with $l = \lceil n^{1/3} \rceil$, %\mc{replaced $\phi$ here, as I understand
%it, we are not using $\phi$ in reference to the temporal dependence of the 
%exponentially distributed series?}, 
as well as 95\%
confidence intervals of the real coverage are displayed in 
\textbf{Figure~\ref{fig:exp1}}.

\section*{simulation results}
\label{sec:simres}

%\subsection*{Results}

@@

For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:norm1}} suggests 
that all methods eventually approach correct coverage of $\mu$ as sample size 
increases. Student's $t$ CIs appear to need the smallest sample size to achieve 
correct coverage, except for samples with strong negative dependence, in which 
case, they actually over-cover $\mu$ for smaller sample sizes. For instance, for 
a sample with $n = 100$ and $\phi = -0.4$, the lower bound for a Students $t$ 
CI's coverage of $\mu$ is greater than 95\%, whereas the coverage intervals for 
other methods contain 95\%. The standard normal, percentile, BC, and BCA, and 
recentered percentile CIs require similar sample sizes to recover $\mu$ at the 
nominal level for all combinations of $n$ and $\phi$. All methods seem to 
require a smaller sample to recover $\mu$ at the nominal rate when dealing with 
negative dependence versus positive dependence. For example, BC CIs recover 
$\mu$ for $n \geq 100$ when $\phi = -0.2$, but they only recover $\mu$ for 
$n \geq 800$ when $\phi = 0.2$. In addition, as a negative dependence gets 
stronger, holding everything else equal, coverage increases, which lead to the 
Student $t$ CI's aforementioned over-coverage. As a positive dependence gets 
stronger, holding everything else equal, coverage decreases, and a larger sample 
is necessary to recover~$\mu$. A possible explanation for this is that if a 
stationary series has a positive 
autocorrelation, the effective sample
size is decreased, whereas is a series has a negative autocorrelation, the
effective sample size is increased. Additionally, this seems to have a 
greater effect on the the estimation of the location parameter versus that
of the scale parameter or temporal dependence parameter.

@@

It appears that a greater sample size is generally required for the bootstrap
CIs to cover the mean and standard deviation parameters in the exponential
margin case than in the normal margin case. In contrast to the marginal normal
distribution, where standard normal, Student's $t$, and 
recentered percentile CI coverage rates were greater for stronger dependences 
regardless of the sign, coverage rates for these CIs seem to be greater only for 
stronger 
negative
dependencies and lesser for stronger positive dependences. 
\mc{What could be an explanation for this?}
However, the other 
trends 
and patterns
discussed in the main text regarding the performance of various methods and
diverse parameters remain consistent. For example, Student's $t$ confidence
intervals still exhibit higher coverage rates in comparison to alternative
methods. Performance continues to be more favorable when temporal dependence is
negative rather than positive. Of particular significance, the 
percentile, BC,
and BCA confidence intervals still display a decline in coverage accuracy for
the lag-1 autocorrelation coefficient as sample size increases as demonstrated
in Figure~\ref{fig:eri}. Both the percentile and BC intervals persist in
manifesting the same bias issue. On the other hand, the recentered percentile
confidence interval continues to be effective in estimating the temporal 
dependence 
due to the
inherent unbiasedness of the original point estimator. In sum, 
for the most part, the findings for
series that are marginally exponentially distributed closely mirror those
attained for series that are marginally normally distributed.

\section*{discussion}
\label{sec:disc}

Block bootstrap is a useful method for estimating parameters of a time series,
from simple parameters like the mean to more complicated temporal dependence
factors. We know theoretically that the block bootstrap procedure will cover a 
parameter of a time series at the nominal level given an infinitely large 
sample, \citep{calhoun2018} so the goal for this study was to find the smallest 
finite sample length 
$n$ of a time series in order for the block bootstrap procedure to recover its 
associated parameters at an acceptable rate. Our analysis relies on the 
assumption that there is a size $n$ large enough for the method to work: that 
is, the method's performance improves as $n$ increases. Out of the six types of 
intervals used in this study, this assumption was found to hold true with 
respect to estimating $\phi$ only for standard normal, Student's $t$, and recentered 
percentile CIs, whereas percentile, BC, and BCA intervals exhibited coverage 
deterioration as $n$ increased. The percentile CI's coverage deterioration can 
be attributed to bias that is not corrected as $n$ increases. Specifically, as 
$n$ increases, the width of the CI decreases, but because the percentile CI 
underestimates $\phi$, the coverage decreases. The BC CI seems to correct the 
bias, but the width of the CI seems to be inconsistent. The acceleration factor 
of the BCA CI seems to fail, as the width of the CI seems to be inconsistent.

>>>>

% control floats
\renewcommand\floatpagefraction{.9}
\renewcommand\topfraction{.9}
\renewcommand\bottomfraction{.9}
\renewcommand\textfraction{.2}
\setcounter{totalnumber}{50}
\setcounter{topnumber}{50}
\setcounter{bottomnumber}{50}

@@

\section*{Introduction}

Block bootstrap is a tool to construct confidence intervals (CI) to make
inferences about dependent data. Essentially, it depends on correct estimation
of the uncertainty in the estimation, similar to the standard bootstrap 
\citep{efron1979bootstrap}, but for serially dependent data.
Early ideas of block bootstrap were developed not long after the standard 
bootstrap.\citep{hall1985resampling, carlstein1986use,kunsch1989jackknife} It 
has since
been applied in various fields, for instance, econometrics and 
meteorology.\citep{mackinnon2006bootstrap, varga2017generalised}
Block bootstrap is especially useful for serially dependent data when the serial 
dependence is not specified or not of primary interest. The method is expected 
to produce CIs with coverage rates matching their nominal levels as the sample 
size grows. However, when dealing with finite sample sizes, an important 
question is how large the sample size must be for block bootstrap CIs to have 
the desired coverage rates.

@@

@@

\section*{Block Bootstrap CIs}
\label{sec:bbci}

@@

\paragraph{Standard Normal CI}
Assuming that $\hat\theta_n$ is asymptotically normally distributed with 
$\theta$ as the mean, we just need an estimate of the standard error to 
construct an approximate CI.\citep{efron1993introduction} Let
$\widehat{\text{SE}}$ be the empirical standard error of the bootstrap point 
estimates $\hat\theta_n^{(b)}$ for $b \in \{1, \ldots, B\}$. Let $z_{(\alpha)}$ 
be the quantile function $F^{-1}(\alpha)$ of the standard normal distribution. 
A $(1 - \alpha)100\%$ standard normal CI is
\[
(\hat{\theta}_{n} - z_{(1-\alpha/2)}\widehat{\text{SE}}, \quad
\hat{\theta}_{n} - z_{(\alpha/2)}\widehat{\text{SE}}).
\]
This CI is centered by the original point estimate $\hat\theta_n$ and is 
symmetric. The standard CI is classified by \citet{efron1993introduction} 
as a confidence interval based on bootstrap ``tables", which essentially means 
it is based on an asymptotic 
distribution with an estimated asymptotic variance (standard error). Its 
validity relies on whether the distribution of $\hat\theta_n$ is reasonably well 
approximated by its asymptotic normal distribution and whether the bootstrap
$\widehat{\text{SE}}$ approximates the true standard error.

\paragraph{Student's $t$ CI}
The procedure for constructing a Student's $t$ CI based on standard bootstrap is 
described in \citet{efron1993introduction}. Let $t_{(\alpha, k)}$ be the 
quantile function $F^{-1}(\alpha, k)$ of a $t$ distribution with $k$ degrees of 
freedom. With 
block bootstrapping, 
a $(1 - \alpha)100\%$ Student's $t$ CI is
\[
(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}\widehat{\text{SE}}, \quad
\hat{\theta}_{n} - t_{(\alpha/2), k -1}\widehat{\text{SE}}),
\]
where $k$ is the number of blocks. This CI is centered by the original point 
estimate $\hat\theta_n$ and is symmetric. Like the standard normal interval, the
Student's $t$ CI is classified by \citet{efron1993introduction} 
as a confidence interval based on bootstrap ``tables". In this case, its 
validity relies on whether the distribution of $\hat\theta_n$ is reasonably well 
approximated by the $t_{k-1}$ distribution with an expected value of $\theta$ 
and whether the bootstrap $\widehat{\text{SE}}$ approximates the true standard 
error.

@@

\paragraph{Bias-Corrected (BC) CI}
The procedure for constructing a bias-corrected Bootstrap CI based on standard
bootstrap is described in \citet{carpenter2000bootstrap}. Let
$\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for
$b \in \{1, \ldots, B\}$. Define 
$\alpha_1 = \Phi(2\hat{z}_0 - z_{1 - \alpha/2})$ 
and $\alpha_2 = \Phi(2\hat{z}_0 - z_{\alpha/2})$. 
A $(1 - \alpha)100\%$ ~BC CI is
\[
(\hat\theta_{n, \alpha_1}^{B}, \quad \hat\theta_{n, \alpha_2}^{B}).
\]

\paragraph{Bias-Corrected and Accelerated (BCA) CI}
The BCA CI was first suggested in \citet{efron1987better}. Let $Z_{(i)}$ be the 
original sample without the $i$th block $z_i$ for $i \in \{1, \ldots, k\}$, let 
$\hat{\theta}_{(i)}$ be the statistic of $Z_{(i)}$, and let 
$\hat{\theta}_{(.)} = k^{-1}\sum_{i=1}^{k} \hat{\theta}_{(i)}$. 
Let
\begin{equation*}
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^2\}^{3/2}}.
\end{equation*}
Define
\begin{equation*}
\alpha_1 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
  z_{\alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{\alpha/2})}\right)
\end{equation*}
and
\begin{equation*}
\alpha_2 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{1 - \alpha/2})}\right).
\end{equation*}
A $(1 - \alpha)100\%$ ~BCA CI is
\[
(\hat\theta_{n, \alpha_1}^{B}, \quad \hat\theta_{n, \alpha_2}^{B}).
\]
This CI is not necessarily centered by $\hat\theta_n$. The BCA method corrects 
for bias and skewness of the $B$ bootstrap point estimates 
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including 
bias-correction and acceleration factors. The acceleration factor refers to the 
rate of change of the standard error of $\hat\theta_n$ with respect to $\theta$.

@@

\section*{Simulation Design}
\label{sec:simdes}

We compared the performance of the different block bootstrap CI methods
under two marginal distributions: normal and exponential.

We generated time series $X_t$ from a 1st 
order autoregressive (AR(1)) process:
\begin{equation*}
X_t = \phi X_{t-1} + \epsilon_t,
\end{equation*}
where $\phi$ is an autoregressive coefficient, and $\epsilon_t$ is a series of
independent errors from a normal distribution with mean zero and variance
$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
$\phi$, which was set to five levels: $\{-0.4, -0.2, 0.0, 0.2, 0.4\}$. We only
used serial dependences as strong as 0.4, because we only seek to 
establish the 
general trend as the strength of the autocorrelation 
increases, and how it varies depending on the sign of the autocorrelation and 
the parameter of interest. The 
series $X_t$ has mean zero and variance 
$\sigma_x^2 = (1 - \phi^2) \sigma_{\epsilon}^2$, so for each value of $\phi$, we 
set $\sigma_{\epsilon}^2 = 1 / (1 - \phi^2)$ such that $\sigma_x^2 = 1$.

Three target parameters of $X_t$ were considered:
1) $\mu = 0$, the mean of $X_t$;
2) $\sigma_x = 1$, the standard deviation of $X_t$; and
3) $\phi$, the lag-1 autocorrelation coefficient.
To investigate the effect of sample size~$n$, we considered an array of values
$n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we generated 
10,000 replicates. The 
block bootstrap sampling step was done with function \texttt{tsboot} from R 
package \textsl{boot},\citep{boot} with block size $\lceil n / l \rceil$. This 
function by default is an implementation of moving block bootstrap as described 
in the previous section, meaning that that blocks are allowed to wrap around, 
and we tried both $l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$,
keeping the order of the block size constant but varying the coefficient. 
For each replicate, we constructed 
six 95\% block bootstrap 
CIs for each parameter as described in the last section with $B = 1000$. We can
estimate $\mu$, $\sigma_x$, and $\phi$ by computing the sample mean,
sample standard deviation, 
and lag-1 autocorrelation, respectively, of each bootstrap sample. Then we can 
construct intervals for each parameter using the appropriate procedures 
described in \textit{Block Bootstrap CIs}. 
Then we estimated their actual coverage 
rates along with their 95\% confidence intervals from the 10,000 replicates.

The coverage rates of the CIs were used to compare the performance of CIs. Let
$\hat\theta_{L, r}$ and $\hat\theta_{U, r}$ be the lower and upper bound,
respectively, for the confidence interval constructed for each replicate
$r \in \{1, \ldots, R\}$, where $R$ is the number of replicates. Then
$cov = \#\{\hat\theta_{L, r} < \theta < \hat\theta_{U, r} \}/R$, for
$r \in \{1, \ldots, R\}$. If a CI method is valid, then the coverage rate is
expected to match the nominal level. Because it is unlikely for the coverage to 
exactly match the nominal level, we can construct a 95\% Wald-type CI of the 
coverage rate 
(which is an estimate of a proportion with $R = 10,000$). If the proportion 0.95 
is included in the interval, the block bootstrap method is likely performing 
well. If all values in the interval are below 0.95, the results would suggest 
that the method either is providing inaccurate estimation, is underestimating 
the process' variability, or a combination of both. If all values in the 
interval are above .95, the results suggest that the method is overestimating 
the process' variability. \citet{brown2001interval} notes that the Wald-type 
interval has poor coverage as the proportion approaches 0 or 1.
\textbf{Figure~\ref{fig:norm1}} 
summarizes the empirical coverage rates and the 95\% confidence intervals of the 
real coverage for a marginal standard normal distribution using block bootstrap
with $l = \lceil n^{1/3} \rceil$, generated using the 
R \textsl{ggplot2} package.\citep{ggplot2}

\subsection*{Marginal Unit Exponential Distribution}
Additionally, to investigate if the results are robust to nonnormal
marginal distributions, we evaluated the performance of block
bootstrap for a time series with a non-normal marginal
distribution. Specifically, we estimated the mean, standard deviation,
and the lag-1 autocorrelation coefficient of a stationary series with
marginal unit exponential distribution. Note that we expect the CIs
that are based on bootstrap ``tables" to depend on the 
asymptotic distribution of the estimator.  This asymptotic
distribution depends more on the sample size than on the marginal
distribution of the time series. So we expect such CIs to 
have similar performance for different marginal distributions when the
sample sizes is large.  The percentile-based CIs (Percentile, BC, BCA,
Recentered Percentile CI) are not necessatily expected to perform
better under non-normal marginal distributions. The student's t and
and normal-based CIs are only noticeably different when the number of
blocks is smaller than 20.

The series were generated by marginally transforming the
AR(1) series $X_t$ in the first simulation study by
\begin{equation*}
W_t = F^{-1}[\Phi(X_t)],
\end{equation*}
where $F^{-1}(p)$ is the quantile function for the unit exponential 
distribution. The true mean ($\mu$) and standard deviation ($\sigma_w$) 
parameters of $W_t$ are~1. The lag-1
autocorrelation coefficient is not invariant to the
transformation,\citep{hofert2018elements} but its value can be obtained by
\begin{equation*}
\int_{-\infty}^\infty \int_{-\infty}^\infty F^{-1}[\Phi(x)] F^{-1}[\Phi(y)] g_2(x, y; \phi) \dd x \dd y - 1,
\end{equation*}
where $g_2(x, y; \phi)$ is the density of a standard bivariate normal
distribution with correlation parameter~$\phi$. We kept the configuration of
$\phi \in \{-0.4, -0.2, 0.0, 0.2, 0.4\}$, and the corresponding lag-1
autocorrelation coefficients are
$\rho \in \{-0.298, -0.156, \allowbreak 0, 0.170, 0.355\}$.

For a marginal exponential  distribution, the empirical coverage rates for 
$\mu$, $\sigma_w$, and 
the lag-1 autocorrelation coefficient $\rho$ using block bootstrap
with $l = \lceil n^{1/3} \rceil$, as well as 95\%
confidence intervals of the real coverage are displayed in 
\textbf{Figure~\ref{fig:exp1}}.

\section*{Simulation Results}
\label{sec:simres}

@@

For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:norm1}} suggests 
that all methods eventually approach correct coverage of $\mu$ as sample size 
increases. Student's $t$ CIs appear to need the smallest sample size to achieve 
correct coverage, except for samples with strong negative dependence, in which 
case, they actually over-cover $\mu$ for smaller sample sizes. For instance, for 
a sample with $n = 100$ and $\phi = -0.4$, the lower bound for a Students $t$ 
CI's coverage of $\mu$ is greater than 95\%, whereas the coverage intervals for 
other methods contain 95\%. The standard normal, percentile, BC, and BCA, and 
recentered percentile CIs require similar sample sizes to recover $\mu$ at the 
nominal level for all combinations of $n$ and $\phi$. All methods seem to 
require a smaller sample to recover $\mu$ at the nominal rate when dealing with 
negative dependence versus positive dependence. For example, BC CIs recover 
$\mu$ for $n \geq 100$ when $\phi = -0.2$, but they only recover $\mu$ for 
$n \geq 800$ when $\phi = 0.2$. In addition, as a negative dependence gets 
stronger, holding everything else equal, coverage increases, which lead to the 
Student $t$ CI's aforementioned over-coverage. As a positive dependence gets 
stronger, holding everything else equal, coverage decreases, and a larger sample 
is necessary to recover~$\mu$. A possible explanation for this is that if a 
stationary series has a positive 
autocorrelation, the effective sample
size is decreased, whereas if a series has a negative autocorrelation, the
effective sample size is increased. Additionally, this seems to have a 
greater effect on the the estimation of the location parameter versus that
of the scale parameter or temporal dependence parameter.

\jy{Are we reporting the C-P intervals? Clarify the desciption and
  cite the reference.}

@@

It appears that a greater sample size is generally required for the bootstrap
CIs to cover the mean and standard deviation parameters in the exponential
margin case than in the normal margin case. In contrast to the marginal normal
distribution, where standard normal, Student's $t$, and 
recentered percentile CI coverage rates were greater for stronger dependences 
regardless of the sign, coverage rates for these CIs seem to be greater only for 
stronger negative dependencies and lesser for stronger positive dependences. 
\mc{What could be an explanation for this?}
\jy{I don't follow this. Are you talking about mu only? Even for mu,
  the statement does not look right.}
\jy{This would invalidate our explanation using the effective sample
  size. Let's tune it down or remove it.}
However, the other 
trends 
and patterns
discussed in the main text regarding the performance of various methods and
diverse parameters remain consistent. For example, Student's $t$ confidence
intervals still exhibit higher coverage rates in comparison to alternative
methods. Performance continues to be more favorable when temporal dependence is
negative rather than positive. Of particular significance, the percentile, BC,
and BCA confidence intervals still display a decline in coverage accuracy for
the lag-1 autocorrelation coefficient as sample size increases as demonstrated
in Figure~\ref{fig:eri}. Both the percentile and BC intervals persist in
manifesting the same bias issue. On the other hand, the recentered percentile
confidence interval continues to be effective in estimating the temporal 
dependence due to the
inherent unbiasedness of the original point estimator. In sum, 
for the most part, the findings for
series that are marginally exponentially distributed closely mirror those
attained for series that are marginally normally distributed.

\section*{Discussion}
\label{sec:disc}

Block bootstrap is a useful method for estimating parameters of a time series,
from simple parameters like the mean to more complicated temporal dependence
factors. We know theoretically that the block bootstrap procedure will cover a 
parameter of a time series at the nominal level given an infinitely large 
sample,\citep{calhoun2018} so the goal for this study was to find the smallest 
finite sample length 
$n$ of a time series in order for the block bootstrap procedure to recover its 
associated parameters at an acceptable rate. Our analysis relies on the 
assumption that there is a size $n$ large enough for the method to work: that 
is, the method's performance improves as $n$ increases. Out of the six types of 
intervals used in this study, this assumption was found to hold true with 
respect to estimating $\phi$ only for standard normal, Student's $t$, and recentered 
percentile CIs, whereas percentile, BC, and BCA intervals exhibited coverage 
deterioration as $n$ increased. The percentile CI's coverage deterioration can 
be attributed to bias that is not corrected as $n$ increases. Specifically, as 
$n$ increases, the width of the CI decreases, but because the percentile CI 
underestimates $\phi$, the coverage decreases. The BC CI seems to correct the 
bias, but the width of the CI seems to be too short. The acceleration factor 
of the BCA CI seems to fail, as the width of the CI seems to be too
short.
\jy{Inconsistent means not consistent and consistency is a desired
  property of an estimator. When we talk about width of a CI, what
  does consistency mean? Do an throughout check, please.}
